Visualizing the Geography of Genetic Variants

### 2016-06-30 paper.Rmd
fixed a few typos

The geographic distribution of rare genetic variants (minor allele frequency $\leq .05$) can be particularly informative in determining an individual's ancestry. Rare variants tend to be localized in small geographic regions because they have arisen recently in human history and have had little time to spread across populations through migration @nelson2012abundance, @mathieson2014demography. Thus by surveying the collection of rare variants that an individual carries provides information about the population origins of that individual's recent ancestors. One of us (J.N.) recently took advantage of the geographic clustering of an individual's rare variants in helping to reaffirm the historically highly contested Native American ancestry of the Kennewick Man, an ancient individual from Washington State @KennewickManReport.

@@

## Query API by rsid {-}
```
http://popgen.uchicago.edu/ggv_api/freq_table?data="1000genomes_phase3_table"&rsID=rs1834640
[
  {
    "alleles": ["A", "G"], 
    "pos": ["-15.310139", "13.443182"], 
    "pop": "GWD", 
    "nobs": "226", 
    "xobs": "17", 
    "freqscale": 1, 
    "freq": [0.0752212389381, 0.9247787610619], 
    "chrom_pos": "15:48392165", 
    "rawfreq": 0.0752212389381
  },
  ...
]
```

## Query API by chromosome position {-}

@@

## Randomly query API {-}

>>>>

The geographic distribution of rare genetic variants (minor allele frequency $\leq .05$) can be particularly informative in determining an individual's ancestry. Rare variants tend to be localized in small geographic regions because they have arisen recently in human history and have had little time to spread across populations through migration events @nelson2012abundance, @mathieson2014demography. Thus by surveying the collection of rare variants that an individual carries provides information about the population origins of that individual's recent ancestors. One of us (J.N.) recently took advantage of the geographic clustering of an individual's rare variants in helping to reaffirm the historically highly contested Native American ancestry of the Kennewick Man, an ancient individual from Washington State @KennewickManReport.

@@

## Query by rsid {-}
```
http://popgen.uchicago.edu/ggv_api/freq_table?data="1000genomes_phase3_table"&rsID=rs1834640
[
  {
    "alleles": ["A", "G"], 
    "pos": ["-15.310139", "13.443182"], 
    "pop": "GWD", 
    "nobs": "226", 
    "xobs": "17", 
    "freqscale": 1, 
    "freq": [0.0752212389381, 0.9247787610619], 
    "chrom_pos": "15:48392165", 
    "rawfreq": 0.0752212389381
  },
  ...
]
```

## Query by chromosome position {-}

@@

## Random query {-}

### 2016-06-30 paper.tex
fixed a few typos

The geographic distribution of rare genetic variants (minor allele
frequency \(\leq .05\)) can be particularly informative in determining
an individual's ancestry. Rare variants tend to be localized in small
geographic regions because they have arisen recently in human history
and have had little time to spread across populations through migration
{[}4{]}, {[}5{]}. Thus by surveying the collection of rare variants that
an individual carries provides information about the population origins
of that individual's recent ancestors. One of us (J.N.) recently took
advantage of the geographic clustering of an individual's rare variants
in helping to reaffirm the historically highly contested Native American
ancestry of the Kennewick Man, an ancient individual from Washington
State \textbf{???}.

@@

\subsection*{Query API by rsid}\label{query-api-by-rsid}
\addcontentsline{toc}{subsection}{Query API by rsid}

@@

\subsection*{Query API by chromosome
position}\label{query-api-by-chromosome-position}
\addcontentsline{toc}{subsection}{Query API by chromosome position}

@@

\subsection*{Randomly query API}\label{randomly-query-api}
\addcontentsline{toc}{subsection}{Randomly query API}

>>>>

The geographic distribution of rare genetic variants (minor allele
frequency \(\leq .05\)) can be particularly informative in determining
an individual's ancestry. Rare variants tend to be localized in small
geographic regions because they have arisen recently in human history
and have had little time to spread across populations through migration
events {[}4{]}, {[}5{]}. Thus by surveying the collection of rare
variants that an individual carries provides information about the
population origins of that individual's recent ancestors. One of us
(J.N.) recently took advantage of the geographic clustering of an
individual's rare variants in helping to reaffirm the historically
highly contested Native American ancestry of the Kennewick Man, an
ancient individual from Washington State \textbf{???}.

@@

\subsection*{Query by rsid}\label{query-by-rsid}
\addcontentsline{toc}{subsection}{Query by rsid}

@@

\subsection*{Query by chromosome
position}\label{query-by-chromosome-position}
\addcontentsline{toc}{subsection}{Query by chromosome position}

@@

\subsection*{Random query}\label{random-query}
\addcontentsline{toc}{subsection}{Random query}
